---
Title: "Laptop Battery Life"
Author: "Akhil Gaur"
output: html_document
fig_caption: no
keep_md: yes
toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Reading the source file

```{r, echo=TRUE}
laptopBattery <- read.table("laptopBattery.txt", sep = ",",header = F)
head(laptopBattery)
```


##setting the names of column

```{r, echo=TRUE}
library(data.table)
setnames(laptopBattery,old = c('V1','V2'),new = c('charge_time','last_life'))
```


##checking for missing value

```{r, echo=TRUE}
 library(VIM)
 imputation_plot <- aggr(laptopBattery,col = c("blue","red"),
                             numbers = TRUE,sortVars = TRUE,
                             labels = names(laptopBattery),gap = 3,
                             ylab = c("Missing Data","Pattern"))
```                             


##Scatter plot to see the data

```{r, echo=TRUE}
 plot(last_life~charge_time,data = laptopBattery)
```


##From the graph(scatter plot) we can se the maximum battery life 
 is 8 hours when we charge for 4 hrs and above,
so we are taking values only upto 4 hrs of charging.


```{r,echo=TRUE}
laptopBattery1<- subset(laptopBattery,subset=charge_time<= 4)
laptopBattery.lm <- lm(last_life~charge_time,data = laptopBattery1)
fitted(laptopBattery.lm)
```
##Summary of the Model

```{r,echo=TRUE, echo=TRUE}
summary(laptopBattery.lm)
```


##Plotting the parameter of model

```{r,echo=TRUE}
layout(matrix(c(1,2,3,4),2,2))
plot(laptopBattery.lm)
```


##plotting the model 

```{r,echo=TRUE}
layout(1)
plot(laptopBattery1$charge_time,laptopBattery1$last_life)
abline(laptopBattery.lm)
```



##Printing the value of model for given input

```{r,echo=TRUE}
input_time <-  data.frame("charge_time" = 1.5)
output_time <- ifelse(input_time<=4,predict(laptopBattery.lm,input_time),8)
print(output_time)
```
